### 2023-10-10 3.Design/wei2res.tex
Pause midi
New wei2res

By solving \cref{eq:wei2res01}, we find the \cref{eq:wei2res2} that gives the values for $R_-$ and $R_+$. All the steps for solving the equations can be found in .%TODO solve equations in appendix

The real value to voltage conversion (\cref{tab:valConv}) doesn't affect this part of the system as the crossbar array already works in voltages. Placing $w$ from \cref{eq:wei2res0} in \cref{eq:doubleMem2} would not change the result.

@@

For the thesis, this step is done in python (TODO show function). Since the resistance resolution is of about%TODO check memristor precision
, the python code then reproduces this by limiting the amount of significant digit of the resistance.

>>>>

By solving \cref{eq:wei2res01}, we find the \cref{eq:wei2res2} that gives the values for $R_-$ and $R_+$. All the steps for solving the equations can be found in \cref{apsec:wei2res}.

The real value to voltage conversion (\cref{tab:valConv}) doesn't affect this part of the system as the crossbar array already works in voltages. Replacing the resistor variable in \cref{eq:doubleMem2} by $w$ using \cref{eq:wei2res0} would not change the results.

@@

While solving the system (\cref{apsec:wei2res}), we get two potential equations for $R_+$. Graphing them shows that one of them is outside of the memristor's resistance range ($[R_{min},R_{max}]$). Leaving us with only one equation because the other one is physically unreachable.

For the thesis, this step is done in python and integrated in the netlist generator script (\cref{sec:netlist}). Since the resistance resolution is of about%TODO check memristor precision
, the python code then reproduces this by limiting the amount of significant digit of the resistance.
